\begin{problem}{Race day in Berland}{stdin}{stdout}{2 seconds}



It is race day in a famous Berland city. 
The city has $n$ junctions and $n-1$ roads connecting these junctions. 
As any well designed city, you can reach any junction from any other by taking a succession of roads. 

Race day consists of $k$ races which takes place during a single day. The $i-th$ race starts at the junction $x_i$, ends at the junction $y_i$ and $c_i$ cars will be participating in it. These cars will start on $x_i$ and they will have to go to the junction $y_i$ using some roads. 


Sadly today is also the day when the road network reparations start. One road has to be rebuilt thus we have to cancel every race which cannot avoid using this road. 
The mayor has asked you to pick the road such that the maximum number of drivers can still run today.

\InputFile

The first line contains $n$, the number of junctions in the city.\\ 
Each of the next $n-1$ lines describes a road.
The $i$-th line contains 2 integers $a_i$ and $b_i$, the two endpoints of the $i$-th road.
The next line contains a single integer $k$, the number of races.\\ 
Each of the next $k$ lines describes a race.\\ 
The $i$-th line contains 3 integers, $x_i$, $y_i$ and $c_i$.

The constraints are as follows:\\ 
$2\le n \le 1\times 10^5$,\\ 
$1\le a_i,b_i\le n, a_i\not = b_i$,\\ 
$0\le k \le 2\times 10^5$,\\ 
$1\le x_i,y_i\le n, x_i\not = y_i$,\\ 
$1\le c_i \le 2\times 10^3$ 


\OutputFile
Print two numbers on a single line separated by a space, the maximum number of drivers who will be able to run and the id of the road which should be rebuilt today (the id is the number of line where the road was described, $1$-indexed and starting from the first road).

If there is more than one possible road, choose the one with the lowest id.

\Example

\begin{examplewide}
\exmp{
5
1 3
4 1
3 5
2 3
3
2 5 7
2 4 5
4 2 5
}{
10 3
}%
\end{examplewide}

The road to rebuild is between the junction number $3$ and $5$.

\end{problem}
