\begin{problem}{Bad divisor}{stdin}{stdout}{6.0 seconds}


Little Petya really hates some number $z$. He defines the score of an integer $x$ as the number of time $z$ divides such integer.
More formally, the score of $x$ is the largest integer $y$ for which $z^y$ divides $x$.

Today little Petya is on the top-left cell (coordinates $(1,1)$) of a grid with $r$ rows and $c$ columns with a number inside each cell.
He can only move one cell down or one cell to the left, without ever going outside the grid. 
He keeps moving until he reaches the bottom-right cell (coordinates $(r,c)$) of the grid. 
\par When he is on the bottom-right cell, he is given a number which is the product of every integer he has been on during his epic journey. 
\par Help him find the minimum score he can achieve.


\InputFile

On the first line, 3 integers representing $r,c$ and $z$.
Each of the next $r$ lines contains $c$ integers.
The $j-th$ integer $a_{ij}$ of the $i-th$ line corresponds to the number is the cell $(i,j)$ of the grid.


The constraints are as follows:
$1\le r,c \le 1000$,\\ 
$1\le z \le 5\times 10^4$,\\ 
$0\le a_{ij} \le 10^{18}$,\\ 

Please use \%Ld modifiers or cin/cout to handle 64-bit integers IO in C/C++

\OutputFile

Print a single integer, the minimum score achievable for little Petya.
If the answer is not defined (goes to infinity), print "-1".

\Example

\begin{examplewide}
\exmp{
2 2 2
2 6
4 5
}{
2
}%
\end{examplewide}

Little Petya starts on the cell with the number $2$ and should end on the cell with number $5$.
\par In order to minimize his score, he should go to the left at the beginning, visiting the cell with number $6$. Like this, he will be given the integer $40$ which has a score 2.
\par If he went down at the beginning, he would have had a score of 3.

\end{problem}
