\begin{problem}{Interactive Permutation Guessing}{standard input}{standard output}{2 seconds}

% Original idea : Mikhail Dvorkin
% Text          : Mikhail Dvorkin
% Tests         : Mikhail Dvorkin

There is a permutation $a$ of size $n$ that you have to guess interactively.

You are allowed to make queries of the following kind. You output any permutation $b$ of size $n$.
The information given back to you is the length of the longest common subsequence of
permutations $a$ and $b$.

\Interaction

First, your program must read from the standard input one line with integer $n$,
the size of the permutation you have to guess.

Your program must then write to the standard output one line with a permutation
and wait for a line in the standard input with a response, then write next query and read next
response, and so on until you know $a$.

Once you receive response $n$ (which means you've found $a$), you're done and
your program must exit.

\InputFile

The first line of the standard input contains integer $n$, the size of the permutation
($1 \le n \le 40$).

Each of the next lines of the standard input contains response to your query~--- the length
of the longest common subsequence of the permutation queried by you and the permutation $a$.

\OutputFile

Each line of the standard output should contain a space-separated list of integers
that form a permutation you're querying.

Your can make at most $5n^2$ queries.

You must flush the standard output after printing each line. You must not print any lines
after you receive the response $n$, just exit.

\Example

\begin{example}
\exmp{
4
3
2
2
4
}{
1 2 3 4
1 3 4 2
4 1 2 3
3 1 2 4
}%
\end{example}

\end{problem}
